### 2015-11-05 CVPR16/Source/intro.tex
Finish Intro

In this work, we first propose to model objects as 3D ellipsoids. Motivated by image formulation theory in computer graphics, we then develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities, which can explicitly explain image observations and reason about object occlusions. Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}. As we will show in the experiments, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for resolving occlusions. Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art motion segmentation methods~\cite{Rao_etal_2010,Brox_Malik_2010}.

As an important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving. In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., $\{0,1\}$ probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [$0,1$] probabilities). Consequently, it offers a unified continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective optimization tools. As we will show later, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of the baseline method~\cite{Song_Chandraker_2014} which employs the bounding box baseline method for point-to-object association.

>>>>

In this work, we first propose to model objects as 3D ellipsoids. Motivated by image formulation theory in computer graphics, we then develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities, which can explicitly explain image observations and reason about object occlusions. Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}. As we will show later, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for tackling occlusions. Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art motion segmentation methods~\cite{Rao_etal_2010,Brox_Malik_2010}.

As an important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving. In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., $\{0,1\}$ probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [$0,1$] probabilities). Consequently, it offers a unified continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective optimization tools. As we will show in the experiments, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of~\cite{Song_Chandraker_2014} which employs bounding boxes for point-to-object assignments.
